Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-26 article/article.tex
(+) added ref to partitions par
(+) Personal settings regarding headings
(+) added par on theoretical performances

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{unicode-math}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algorithm,algpseudocode}
\usepackage{paralist}

@@

%\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry}
%\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption}
%\usepackage{booktabs}
%
%\usepackage{lettrine}
%
%\usepackage{enumitem}
%\setlist[itemize]{noitemsep}
%
%\usepackage{abstract}
%% Set the "Abstract" text to bold
%\renewcommand{\abstractnamefont}{\normalfont\bfseries}
%% Set the abstract itself to small italic text
%\renewcommand{\abstracttextfont}{\normalfont\small\itshape}
%
%% Allows customization of titles
%\usepackage{titlesec}
%
%% Headers and footers
%\usepackage{fancyhdr}
%% All pages have headers and footers
%\pagestyle{fancy}
%% Blank out the default header
%% \fancyhead{}
%% Blank out the default footer
%\fancyfoot{}
%% Custom header text
%% \fancyhead[C]{Running title $\bullet$ May 2016 $\bullet$ Vol. XXI, No. 1}
%% Custom footer text
%\fancyfoot[RO,LE]{\thepage}
%\usepackage{titling} % Customizing the title section

@@

%-----------------------------------------------------------------------------
%	TITLE SECTION
%-----------------------------------------------------------------------------

%% Move the title up
%\setlength{\droptitle}{-4\baselineskip}
%% Article title formatting
%\pretitle{\begin{center}\Huge\bfseries}
%% Article title closing formatting
%  \posttitle{\end{center}}

%\renewcommand{\maketitlehookd}{%
%  \begin{abstract}
%
%  \end{abstract}
%}

%-----------------------------------------------------------------------------
\begin{document}

@@

@@

\subsubsection{Partitions}

>>>>

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{unicode-math}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algorithm,algpseudocode}
\usepackage{paralist}
\usepackage{titlesec}

@@

% Headings customisation
\titleformat*{\section}{\Large\scshape\center}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\Alph{subsection}}

@@

\begin{document}

@@

\subsection{Theoretical performances}
In this paper, we consider a high branching factor problem.

Let \(M\) be the number of edges between the inital state and a final state and
\(K\) the branching factor.
Then, the complexity of the A\(^*\) is expected to be, in the worst case,
exponential in \(M\) (see~\cite{alliotschiex2002ia&it}).

Since the Monte carlo tree is a stochastic method, one must wait for a
satisfactorily converging solution rather than the exact solution. It has
however been proven in~\cite{kocsis2006bandit} that the bias of the expected
payoff is \(O\left(\frac{\log n}{n}\right)\). Furthermore, the failure
probability\footnote{probability of not selecting the best child} converges to
zero at a polynomial rate.

@@

\subsubsection{Partitions}\label{ssec:partitions}
